---
title: "DSApps 2020 @ TAU: Assignment 3"
author: "Giora Simchoni"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
subtitle: The Tidyverse - Part C
---

```{r child = "setup.Rmd"}
```

### Welcome

Welcome to Assignment 3 in R!

Remember:

* You can play with the assignment in Playground mode, but:
* Only your private Github repository assigned to you by the course admin will be cloned and graded (Submission mode, see instructions [here](https://github.com/DSApps-2020/Class_Slides/blob/master/Apps_of_DS_HW.pdf))
* Like any other University assignment, your work should remain private
* You need to `git clone` your private Github repository locally as explained [here](https://github.com/DSApps-2020/Class_Slides/blob/master/Apps_of_DS_HW.pdf)
* You need to uncomment the starter code inside the chunk, replace the `### YOUR CODE HERE ###`, run the chunk and see that you're getting the expected result
* Pay attention to what you're asked to do and the required output
* For example, using a *different* function than the one you were specifically asked to use, will decrease your score (unless you amaze me)
* Your notebook should run smoothly from start to end if someone presses in the RStudio toolbar Run --> Restart R and Run All Chunks
* When you're done knit the entire notebook into a html file, this is the file that would be graded
* You can add other files but do not delete any files
* Commit your work and push to your private Github repository as explained [here](https://github.com/DSApps-2020/Class_Slides/blob/master/Apps_of_DS_HW.pdf)

This assignemtnt is due: 19/4 23:59

### Packages

These are the packages you will need. If you don't have them, you need to uncomment the `install.packages()` line and install them first (you can also just copy this command to the R console and do it there if you don't want all the output printed in this notebook).

When you load the packages you may see different kinds of messages or warnings, skim them:

```{r}
# install.packages(c("tidyverse"))
library(tidyverse)
```
